Modelling potential environmental impacts of science activity in Antarctica

### 2025-06-07 paper/paper.qmd
updated gitignore

---
title: Modelling potential environmental impacts of science activity in Antarctica
author: 
  - name: David O’Sullivan
    email: david.osullivan@auckland.ac.nz
    affiliations:
      - name: University of Auckland
        url: https://profiles.auckland.ac.nz/david-osullivan
      - name: Geospatial Stuff 
        url: https://dosull.github.io
  - name: Fraser J. Morgan
    affiliations: 
      - name: Manaaki Whenua Landcare Research 
        url: https://landcareresearch.co.nz
bibliography: antarctica.bib
csl: the-canadian-geographer.csl
lightbox: true
navbar: false
sidebar: false
format: 
  typst:
    toc: false
    number-sections: true
    fig-format: png
    fig-dpi: 600
  html:
    toc: true
    # code-fold: true
    number-sections: true
    number-depth: 3
    self-contained: true
  # pdf:
  #   documentclass: article
  #   classoption: [11pt]
  #   toc: false
  #   number-sections: true
  #   number-depth: 3
  #   linestretch: 1.15
execute:
  echo: false
  warning: false
  results: false
  message: false
  cache: true
  freeze: auto
---

>>>>

---
title: Modelling potential environmental impacts of science activity in Antarctica
author: 
  - name: David O’Sullivan
    email: david.osullivan@auckland.ac.nz
    affiliations:
      - name: University of Auckland
        url: https://profiles.auckland.ac.nz/david-osullivan
      - name: Geospatial Stuff 
        url: https://dosull.github.io
  - name: Fraser J. Morgan
    affiliations: 
      - name: Manaaki Whenua Landcare Research 
        url: https://landcareresearch.co.nz
bibliography: antarctica.bib
csl: the-canadian-geographer.csl
lightbox: true
navbar: false
sidebar: false
format: 
  typst:
    toc: false
    number-sections: true
    fig-format: png
    fig-dpi: 600
  html:
    toc: true
    # code-fold: true
    number-sections: true
    number-depth: 3
    self-contained: true
execute:
  echo: false
  warning: false
  results: false
  message: false
  cache: true
  freeze: auto
---
